GPU-Accelerated Parallelization of Edge-Based Motion Detection Algorithms with the NVIDIA CUDA Framework

### 2015-12-05 documents/paper/paper.tex

\section{Introduction}
Graphics processing units (GPUs) are rapidly gaining popularity as a platform for parallelized computations on massive sets of data. Since much of the computations in image processing and computer vision are easily parallelized, graphics operations on GPUs achieve significant speedups compared to those done on their serial, CPU counterparts. Further, SDKs like the NVIDIA CUDA framework provide developers easy APIs to take advantage of the parallel computing power of GPUs. We take full advantage of the computational benefits of GPUs by implementing edge detection and motion detection algorithms in CUDA C.

@@

\subsection{GPU Parallelization and CUDA Implementation}
Placeholder text

>>>>

\section{Introduction}
Graphics processing units (GPUs) are rapidly gaining popularity as a platform for parallelized computations on massive sets of data. Since much of the computations in image processing and computer vision are easily parallelized, graphics operations on GPUs achieve significant speedups compared to those done on their serial, CPU counterparts. Further, SDKs like the NVIDIA CUDA framework provide developers easy APIs to take advantage of the parallel computing power of GPUs. We take full advantage of the computational benefits of GPUs by implementing edge detection and motion detection algorithms in CUDA C.
\par In this paper, we first detail the theory for our edge detection and motion detection algorithms. Then, we describe the GPU code implementation of those algorithms with NVIDIA CUDA. Finally, we present speedup results achieved by our CUDA implementation with respect to a reference serial, CPU implmentation.

@@

\subsection{GPU Parallelization and CUDA Implementation}
Our CUDA implementation of our motion detection algorithm is similar to that for our implementation of separable convolution and edge detection. Using the same 16 threads per block, we divide the input image into the appropriate number of blocks such that the thresholded difference computation at each index $(i, j)$ of Algorithm \ref{difference-matrix-algorithm} has its own thread. Thus, each element of $\boldsymbol{D}$ is calculated in parallel.
\begin{lstlisting}[
	caption=GPU computation of thresholded difference matrix,
	label=difference-filter-implementation
]
__global__ void difference_filter(int *dev_out, int *edges_1, int *edges_2, int width, int height, int threshold) {
	const int r = blockIdx.y * blockDim.y + threadIdx.y;
	const int c = blockIdx.x * blockDim.x + threadIdx.x;
	const int i = r * width + c;

    // Set it to 0 initially
    dev_out[i] = 0;
    int crop_size = 7;
    if (r > crop_size && c > crop_size && r < height - crop_size && c < width - crop_size && edges_1[i] != edges_2[i]) {
        // Set to 255 if there is a pixel mismatch
        dev_out[i] = 255;
        for (int x_apron = -threshold; x_apron <= threshold; x_apron++) {
            for (int y_apron = -threshold; y_apron <= threshold; y_apron++) {
                // Ensure the requested index is within bounds of image
                if (c + x_apron > 0 && r + y_apron > 0 && c + x_apron < width && r + y_apron < height) {
                    // Check if there is a matching pixel in the apron, within the threshold
                    if (edges_1[(r + y_apron) * width + c + x_apron] == edges_2[i]) {
                        // Set it back to 0 if a corresponding pixel exists within the vicinity of the match
                        dev_out[i] = 0;
                    }
                }
            }
        }
    }
}
\end{lstlisting}
